---
title: "Two Pore Guys Dynamic Report"
output: html_document
params:
  Events: df_Event
  Model_file: my_model
  
  Experiment_Info: df_Data_Info
  config: my_config
    
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 14px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>


```{r, echo=FALSE, comment=NA}
library(ggplot2)
library(plotly)
library(htmltools)
library(plyr)

# load data and model
df <- params$Events
df$dset_Exp_bind <- paste(df$setNum, df$Exp, sep = " - ")
dset_Exp <- unique(df[,c("setNum","Exp")])
model <- params$Model_file
if (grepl("rpart", toString(model$call))) {
  # predict_type <- "class"
  class_choices <- attr(model, "ylevels")
} else {
# predict_type <- "raw"
class_choices <- model$levels
}
if (grepl("rpart", toString(model$call))) {
  predict_type <- "class"
} else {
predict_type <- "raw"
}

my_paras <- params$config
```

---


<center><h1>Experiment Information</h1></center>
```{r, echo=FALSE, comment=NA}
Exp_Info <- params$Experiment_Info
cat(paste("Project : ", Exp_Info$project, "\n", sep = ""))
cat(paste("Goal : ", Exp_Info$goal, "\n", sep = ""))
cat(paste("Date : ", Exp_Info$datetime, "\n", sep = ""))
cat(paste("Experimenter : ", Exp_Info$user, "\n", sep = ""))
cat(paste("Pore Number : ", Exp_Info$pore_number, "\n", sep = ""))
cat(paste("Buffer : ", Exp_Info$buffer, "\n", sep = ""))
cat(paste("conductivity : ", Exp_Info$conductivity, "\n", sep = ""))
cat(paste("Pore thickness : ", Exp_Info$thickness, "\n", sep = ""))
cat(paste("Sampling Rate : ", Exp_Info$sample_rate, "\n", sep = ""))
```

---


<center><h2>Assay Information</h2></center>
```{r, echo=FALSE, comment=NA}
knitr::kable(Exp_Info$dsets[,c("index","assay","concentration","control_type","dilution_factor","is_dirty","voltage","pcr_cycle_number")]) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), position = "center")
```

---


<center><h1>Model Information</h1></center>
```{r, plotly=TRUE, echo=FALSE, comment=NA}
x_para <- my_paras$Model_Info$X
y_para <- my_paras$Model_Info$Y
if(my_paras$Model_Info_Enable) {
  cat(paste("Modeling Algorithm : ", my_paras$Model, "\n", sep = ""))
  cat(paste("Modeling Parameters : ", paste(my_paras$Model_Para, collapse = ", "), "\n", sep = ""))
  cat(paste("Modeling Controls sets: ", paste(my_paras$Model_dsets, collapse = ", "), "\n", sep = ""))
  cat(paste("Target Molecule for Q-test : ", my_paras$Target_Molecule, "\n", sep = ""))
  cat(paste("Calibrant Molecule for Q-test : ", my_paras$Calibrant_Molecule, "\n", sep = ""))
  cat("Notes: \n")
  cat(my_paras$Model_Info_Notes)
  cat("\n")
}
```


<center><h2>Scatter Plots for control datasets</h2></center>
```{r, plotly=TRUE, echo=FALSE, message=FALSE}
  df_selected <- df[df$setNum %in% my_paras$Model_dsets,]
  p <- htmltools::tagList()
  p[[1]] <- plot_ly(df_selected, x = df_selected[, x_para], y = df_selected[, y_para], mode = "markers", type = "scatter", color = factor(paste(df_selected$setNum, df_selected$Exp, sep = "-")), colors = "Set1") %>% 
    layout(xaxis = list(title = x_para),yaxis = list(title = y_para),title = "Control samples")
  p
```


---


<center><h1>Scatter Plot(s)</h1></center>
```{r, plotly=TRUE, echo=FALSE, comment=NA}
if(my_paras$Scatter_Plot_Enable) {
  cat(paste("Scatter Plots of samples :", paste(my_paras$Scatter_Plot_dsets, collapse = " , "), "\n", sep = " "))
  cat("Notes: \n")
  cat(my_paras$Scatter_Plot_Notes)
}
```


```{r, plotly=TRUE, echo=FALSE, message=FALSE}
if(my_paras$Scatter_Plot_Enable) {
  df_selected <- df[df$dset_Exp_bind %in% my_paras$Scatter_Plot_dsets,]
  p <- htmltools::tagList()
  p[[1]] <- plot_ly(df_selected, x = df_selected[, x_para], y = df_selected[, y_para], mode = "markers", type = "scatter", color = factor(df_selected$dset_Exp_bind), colors = "Set1") %>% 
    layout(xaxis = list(title = x_para),yaxis = list(title = y_para))
  p
}
```


---


<center><h1>Model Prediction Plot(s)</h1></center>
```{r, plotly=TRUE, echo=FALSE, comment=NA}
if(my_paras$Model_Prediction_Plot_Enable) {
  cat(paste("Model Prediction Plots of samples :", paste(my_paras$Model_Prediction_Plot_dsets, collapse = " , "), "\n", sep = " "))
  cat("Notes: \n")
  cat(my_paras$Model_Prediction_Plot_Notes)
}
```


```{r, plotly=TRUE, echo=FALSE, message=FALSE}
if(my_paras$Model_Prediction_Plot_Enable) {
  dsets <- my_paras$Model_Prediction_Plot_dsets
  l <- htmltools::tagList()
  for(i in 1:length(dsets)) {
    df_selected <- df[df$dset_Exp_bind == dsets[i],]
    class_type <- predict(model, df_selected, type = predict_type)
    l[[i]] <- plot_ly(df_selected, x = df_selected[, x_para], y = df_selected[, y_para], mode = "markers", type = "scatter", color = class_type, colors = "Set1") %>% 
      layout(xaxis = list(title = x_para),yaxis = list(title = y_para),title = paste("dset:", dsets[i], sep = ""))
  }
  l
}
```


---


<center><h1>Q Plot(s)</h1></center>
```{r, plotly=TRUE, echo=FALSE, comment=NA}
if(my_paras$Q_Plot_Enable) {
  cat(paste("Q Plots of samples :", paste(my_paras$Q_Plot_dsets, collapse = ", "), "\n", sep = " "))
  cat(paste("Tareget Molecule : ", my_paras$Target_Molecule, "\n", sep = ""))
  cat(paste("Calibrant Molecule : ", my_paras$Calibrant_Molecule, "\n", sep = ""))
  cat("Notes: \n")
  cat(my_paras$Q_Plot_Notes)
}
```


```{r, plotly=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
if(my_paras$Q_Plot_Enable) {
  dsets <- my_paras$Q_Plot_dsets
  l <- htmltools::tagList()
  
  #Calculate Q-values and error for each dset
  target_molecule <- my_paras$Target_Molecule
  calibrant_molecule <- my_paras$Calibrant_Molecule
  set_list <- dsets
    
  Q_df <- data.frame('index' = as.integer(), 'q_value' = as.double(), 'q_error' = as.double(), 'd_set' = as.integer())
    
  for (sub_set in set_list) {
      df_selected_subset <- df[df$dset_Exp_bind == sub_set,]
      class_type_subset <- predict(model, df_selected_subset, type = predict_type)
      q_value <- vector(length = length(class_type_subset), mode = "double")
      q_error <- vector(length = length(class_type_subset), mode = "double")
      
      num_target <- 0
      num_all <- 0
      for (i in 1:length(class_type_subset)) {
        if(i == 1) {
          q_value[1] <- as.integer(class_type_subset[1] == target_molecule)
          q_error[i] <- 0
          num_target <- as.integer(class_type_subset[1] == target_molecule)
          num_all <- as.integer(class_type_subset[1] == target_molecule | class_type_subset[1] == calibrant_molecule)
          if(num_all == 0) {
            q_value[i] <- 0
            q_error[i] <- 0
          }
          else {
            q_value[i] <- num_target/num_all
            q_error[i] <- 1.96*sqrt(q_value[i]*(1-q_value[i])/num_all)
          }
        } 
        else {
          num_target <- num_target + as.integer(class_type_subset[i] == target_molecule)
          num_all <- num_all + as.integer(class_type_subset[i] == target_molecule | class_type_subset[i] == calibrant_molecule)
          if(num_all == 0) {
            q_value[i] <- 0
            q_error[i] <- 0
          }
          else {
            q_value[i] <- num_target/num_all
            q_error[i] <- 1.96*sqrt(q_value[i]*(1-q_value[i])/num_all)
          }
        }
      }
      Q_df <- rbind(Q_df,data.frame('index' = 1:length(class_type_subset), 
                                    'q_value' = q_value, 
                                    'q_error' = q_error, 
                                    'd_set' = as.vector(rep(sub_set, length(class_type_subset)))))
    }
  # End of calculation
  l[[1]] <- plot_ly(data = Q_df, x = Q_df$index, y = 100*(Q_df$q_value), type = 'scatter', mode='lines', color = Q_df$d_set) %>% add_ribbons(ymin = 100*(Q_df$q_value - Q_df$q_error), ymax = 100*(Q_df$q_value + Q_df$q_error)) %>%
     layout(xaxis = list(title = "Number of events"),yaxis = list(title = "Percentage(%)"), title = "Q-Plots")
  l
}
```

---


<center><h2>Q Values</h2></center>
```{r, echo=FALSE, comment=NA}
Q_df_split <- ddply(Q_df, .(d_set), function(x) x[nrow(x),c('d_set', 'q_value','q_error')])
Q_df_split$q_value <- Q_df_split$q_value*100
Q_df_split$q_error <- Q_df_split$q_error*100
knitr::kable(Q_df_split) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), position = "center")
```